A Comparision of Bootstrap Methods

### 2022-11-30 project/PaperTemplate/paper.Rmd
Updated simulation

library(boot)
set.seed(495)

@@

```{r}
findCIs <- function(sampleinput, trueparameter, nboot) {

  sample_mean <- mean(~ Dec, data = sampleinput)
  sample_sd <- sd(~ Dec, data = sampleinput)
  sample_n <- nrow(sampleinput)

  for (i in 1:nboot) {
    resampled <- as.data.frame(mosaic::resample(sampleinput, replace = TRUE))
    mean[i] <- mean(~ Dec, data = resampled)
    sd[i] <- sd(~ Dec, data = resampled)
    se[i] <- sd[i]/sqrt(nrow(resampled))
    t_stat[i] <- (mean[i] - orig_mean)/se[i]
  }

  # find BCa interval
  theta <- function(x){mean(x)}
  jackknife_results <- bootstrap::jackknife(sampleinput$Dec, theta)
  jackmean <- mean(~ jackknife_results$jack.values)
  estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
    (sum((jackknife_results$jack.values - jackmean)^2))^(1.5)
  a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/(1-estimated_a*(z0 + qnorm(alphalow))))
  a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/(1-estimated_a*(z0 + qnorm(alphahigh))))
  bca_interval <- qdata(~ mean, c(a_newlow, a_newhigh), data = boot_means)

  # find studentized
  q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
  lower <- q[1]
  upper <- q[2]
  t_interval <- c(orig_mean - upper*orig_se, orig_mean - lower*orig_se)

  output <- c(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", "BCa Interval", "Studentized Interval")
  output
}

OUTPUT1 <- findCIs(SnowGR, 0, 10)
```

reps <- 10000
n <- 15

r_pvals <- rep(0, reps)
tau_pvals <- rep(0, reps)

for(i in 1: reps) {
  y <- rgamma(n, 8, 2)

  values <- data.frame(x,y)

  r_pvals[i] <- with(values, cor.test(x, y))$p.value
  tau_pvals[i] <- with(values, cor.test(x, y, method = "kendall"))$p.value
}

sum(r_pvals <= 0.05)/reps
sum(tau_pvals <= 0.05)/reps

>>>>

```{r}
findCIs <- function(sampleinput, nboot) {

  sample_mean <- mean(~ X, data = sampleinput)
  sample_sd <- sd(~ X, data = sampleinput)
  sample_n <- nrow(sampleinput)
  sample_se <- sample_sd/sqrt(sample_n)

  for (i in 1:nboot) {
    resampled <- as.data.frame(mosaic::resample(sampleinput, replace = TRUE))
    mean[i] <- mean(~ X, data = resampled)
    sd[i] <- sd(~ X, data = resampled)
    se[i] <- sd[i]/sqrt(nrow(resampled))
    t_stat[i] <- (mean[i] - sample_mean)/se[i]
  }

  # find BCa interval
  theta <- function(x){mean(x)}
  jackknife_results <- bootstrap::jackknife(sampleinput$X, theta)
  jackmean <- mean(~ jackknife_results$jack.values)
  estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
    (sum((jackknife_results$jack.values - jackmean)^2))^(1.5)
  a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/(1-estimated_a*(z0 + qnorm(alphalow))))
  a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/(1-estimated_a*(z0 + qnorm(alphahigh))))
  bca_interval <- qdata(~ mean, c(a_newlow, a_newhigh), data = boot_means)

  # find studentized
  t_q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
  lower_q <- t_q[1]
  upper_q <- t_q[2]
  t_interval <- c(sample_mean - (upper_q*sample_se), sample_mean - (lower_q*sample_se))
  output <- list(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", "BCa Interval", "Studentized Interval")
  output
}

```{r}
set.seed(495)
#OUTPUT1 <- findCIs(values, 2000)
#OUTPUT1
```

```{r}
# way with boot library
library(boot)
set.seed(495)

@@
